\textbf{NBA Party}

### 2017-06-12 init_model.rnw
Added a plot showing why drinking estabs and population don't work.

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')
musicians <- merge(musicians, pop, by = c('county', 'season'), all.x = T)

@@

>>>>

load(file = 'tmp_data/covers_lines.RData')
## load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')
load(file = 'tmp_data/nba_musicians.RData')

musicians <- copy(dt)
rm(dt)
setnames(musicians, 'variable', 'nmusicians')
musicians <- merge(musicians, pop, by = c('county', 'season'), all.x = T)

@@

##################################################
### Why drinking estabs doesn't work.
##################################################
load(file = 'tmp_data/nba_drinking.RData')
drinking <- copy(dt)
setnames(drinking, 'variable', 'ndrinks')
rm(dt)

tmpm <- musicians[, list(log.nmusicians = mean(log(nmusicians+1)),
                         log.population = mean(log(population))), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log Avg of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)))
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 22.5, y = 10.25, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 24.6, y = 10.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 24.6, y = 11, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
dev.off()
